Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization.

### 2023-02-16 manuscript.Rmd
add acknowledgement
Update manuscript.Rmd
added Centre affiliation

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
author:
  - name: Aaron Peikert
    affil: a, b
    email: peikert@mpib-berlin.mpg.de
  - name: Andreas M. Brandmaier
    affil: a, c
    email: brandmaier@mpib-berlin.mpg.de
affiliation:
  - num: a
    address: |
      Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany
  - num: b
    address: |
      Department of Psychology, Humboldt-Universität zu Berlin, Unter den Linden 6, 10117 Berlin, Germany
  - num: c
    address: |
      MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
    - apa.csl
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
    - curl
    - inkscape
output: rticles::tf_article
type: ARTICLE TEMPLATE
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; bayesian; open science
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
---

@@

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization."
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
author:
  - name: Aaron Peikert
    affil: a, b
    email: peikert@mpib-berlin.mpg.de
  - name: Andreas M. Brandmaier
    affil: a, c, d
    email: brandmaier@mpib-berlin.mpg.de
affiliation:
  - num: a
    address: |
      Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany
  - num: b
    address: |
      Department of Psychology, Humboldt-Universität zu Berlin, Unter den Linden 6, 10117 Berlin, Germany
  - num: c
    address: |
      MSB Medical School Berlin, Rüdesheimer Str. 50, 14197 Berlin, Germany
  - num: d
    address: |
     Max Planck UCL Centre for Computational Psychiatry and Ageing Research Berlin, Germany and London, UK
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
    - apa.csl
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
  tlmgr:
    - pgf
    - preview
    - libertine
  apt:
    - git
    - rsync
    - curl
    - inkscape
output: rticles::tf_article
type: ARTICLE TEMPLATE
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; bayesian; open science
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
---

@@

# Acknowledgement {-}

We thank Maximilian S. Ernst, Caspar van Lissa, Felix Schönbrodt, the discussants at the DGPS2022 conference and Open Science Center Munich, and many more for the insightful discussions about disentangling preregistration and confirmation.
